Draft Final Report: Measles risk assessment, modelling, and benefit--cost analyses for New Zealand

### 2015-03-18 draftfinalreport_v2.tex
revised draft

\usepackage{Sweave}
\begin{document}
\input{draftfinalreport-concordance}

@@

\begin{figure}
\begin{center}
\includegraphics{draftfinalreport-002}
\end{center}
\caption{Numbers and age of measles cases in years in New Zealand for two periods, 1997--2014 and 2007--2014}
\label{fig:ageinyears}
\end{figure}

@@

@@

\begin{figure}
\begin{center}
\includegraphics{draftfinalreport-010}
\end{center}
\caption{Per capita rates of measles infections for specific age categories (0--2, 3--5, 6--17, 18--24, and 24+ years) and New Zealand deprivation indices (NZDep, 1--5 and 6--10) for 2007--2014, broken down by ethnicity (\autoref{table:percap} for details)}
\label{fig:percap}
\end{figure}

\begin{table}[hbtp]
\footnotesize
\caption{Numbers of measles cases (Cases), population sizes (Ppulation) and per capita rates per 10,000 (Per capita) of measles in specific age (Age), ethnicity (Ethnicity) and socio-economic deprivation (NZDep) categories from 2007-2014}
%latex.default(PerCap, file = "", table.env = FALSE, rowname = NULL)%
\begin{center}
\begin{tabular}{lllrrr}
\hline\hline
\multicolumn{1}{c}{NZDep}&\multicolumn{1}{c}{Age}&\multicolumn{1}{c}{Ethnicity}&\multicolumn{1}{c}{Population}&\multicolumn{1}{c}{Cases 1}&\multicolumn{1}{c}{Per capita}\tabularnewline
\hline
1-5&0-2&Asian&$   6094$&$ 11$&$18.0505$\tabularnewline
6-10&0-2&Asian&$   6806$&$  8$&$11.7543$\tabularnewline
1-5&3-5&Asian&$   6094$&$  1$&$ 1.6410$\tabularnewline
6-10&3-5&Asian&$   6806$&$  0$&$ 0.0000$\tabularnewline
1-5&6-17&Asian&$  33918$&$ 11$&$ 3.2431$\tabularnewline
6-10&6-17&Asian&$  28905$&$  5$&$ 1.7298$\tabularnewline
1-5&18-24&Asian&$  22917$&$  3$&$ 1.3091$\tabularnewline
6-10&18-24&Asian&$  34107$&$  5$&$ 1.4660$\tabularnewline
1-5&25+&Asian&$  96357$&$ 10$&$ 1.0378$\tabularnewline
6-10&25+&Asian&$  98715$&$ 13$&$ 1.3169$\tabularnewline
1-5&0-2&European&$  57872$&$ 83$&$14.3420$\tabularnewline
6-10&0-2&European&$  45445$&$ 64$&$14.0830$\tabularnewline
1-5&3-5&European&$  57872$&$ 42$&$ 7.2574$\tabularnewline
6-10&3-5&European&$  45445$&$ 17$&$ 3.7408$\tabularnewline
1-5&6-17&European&$ 264330$&$219$&$ 8.2851$\tabularnewline
6-10&6-17&European&$ 182937$&$ 80$&$ 4.3731$\tabularnewline
1-5&18-24&European&$ 107649$&$ 34$&$ 3.1584$\tabularnewline
6-10&18-24&European&$ 117840$&$ 36$&$ 3.0550$\tabularnewline
1-5&25+&European&$1001916$&$ 78$&$ 0.7785$\tabularnewline
6-10&25+&European&$ 724317$&$ 51$&$ 0.7041$\tabularnewline
1-5&0-2&Maori&$  10003$&$ 18$&$17.9946$\tabularnewline
6-10&0-2&Maori&$  30104$&$ 48$&$15.9447$\tabularnewline
1-5&3-5&Maori&$  10003$&$  7$&$ 6.9979$\tabularnewline
6-10&3-5&Maori&$  30104$&$ 11$&$ 3.6540$\tabularnewline
1-5&6-17&Maori&$  40461$&$ 19$&$ 4.6959$\tabularnewline
6-10&6-17&Maori&$ 116640$&$ 92$&$ 7.8875$\tabularnewline
1-5&18-24&Maori&$  15360$&$  5$&$ 3.2552$\tabularnewline
6-10&18-24&Maori&$  48495$&$  8$&$ 1.6497$\tabularnewline
1-5&25+&Maori&$  71217$&$  2$&$ 0.2808$\tabularnewline
6-10&25+&Maori&$ 192729$&$  6$&$ 0.3113$\tabularnewline
1-5&0-2&MLA&$    728$&$  0$&$ 0.0000$\tabularnewline
6-10&0-2&MLA&$   1290$&$  3$&$23.2558$\tabularnewline
1-5&3-5&MLA&$    728$&$  0$&$ 0.0000$\tabularnewline
6-10&3-5&MLA&$   1290$&$  1$&$ 7.7519$\tabularnewline
1-5&6-17&MLA&$   2991$&$  0$&$ 0.0000$\tabularnewline
6-10&6-17&MLA&$   4539$&$  1$&$ 2.2031$\tabularnewline
1-5&18-24&MLA&$   1710$&$  0$&$ 0.0000$\tabularnewline
6-10&18-24&MLA&$   3078$&$  2$&$ 6.4977$\tabularnewline
1-5&25+&MLA&$   8028$&$  0$&$ 0.0000$\tabularnewline
6-10&25+&MLA&$  10335$&$  6$&$ 5.8055$\tabularnewline
1-5&0-2&Pacific&$   2093$&$  5$&$23.8892$\tabularnewline
6-10&0-2&Pacific&$  13124$&$ 58$&$44.1938$\tabularnewline
1-5&3-5&Pacific&$   2093$&$  0$&$ 0.0000$\tabularnewline
6-10&3-5&Pacific&$  13124$&$  3$&$ 2.2859$\tabularnewline
1-5&6-17&Pacific&$   8541$&$  5$&$ 5.8541$\tabularnewline
6-10&6-17&Pacific&$  51183$&$ 22$&$ 4.2983$\tabularnewline
1-5&18-24&Pacific&$   3972$&$  1$&$ 2.5176$\tabularnewline
6-10&18-24&Pacific&$  22098$&$  8$&$ 3.6202$\tabularnewline
1-5&25+&Pacific&$  18492$&$  2$&$ 1.0815$\tabularnewline
6-10&25+&Pacific&$  91533$&$ 11$&$ 1.2018$\tabularnewline
\hline
\end{tabular}\end{center}\label{table:percap}
\end{table}

@@

The distribution of the meases cases per category used in the regression analyses are in \autoref{fig:histcasecat}.
\begin{figure}
\begin{center}
\includegraphics{draftfinalreport-014}
\end{center}
\caption{Distribution of measles cases per category (\autoref{table:percap}) used in the final regression model (\autoref{eq:reg})}
\label{fig:histcasecat}
\end{figure}

The predicted values from the regression model plotted against the reported cases are shown in \autoref{fig:predict}, and the residuals are shown in \autoref{fig:resid}.
\begin{figure}
\begin{center}
\includegraphics{draftfinalreport-015}
\end{center}
\caption{Regression model (\autoref{eq:reg}) predictions plotted against the case data (\autoref{table:percap})}
\label{fig:predict}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics{draftfinalreport-017}
\end{center}
\caption{Histogram of residuals from the regression model (\autoref{eq:reg})}
\label{fig:resid}
\end{figure}

The significance of the different predictor variables can be seen in the ANOVA results (\autoref{table:anova}).
\par
\vspace{5mm} %5mm vertical space
\begin{table}
% latex table generated in R 3.0.2 by xtable 1.7-1 package
% Mon Nov 10 12:38:31 2014
\begin{tabular}{lrrrrrr}
  \hline
 & Df & Deviance & Resid. Df & Resid. Dev & F & Pr($>$F) \\ 
  \hline
NULL &  &  & 39 & 1453.62 &  &  \\ 
  Age & 4 & 1304.20 & 35 & 149.43 & 183.58 & 0.0000 \\ 
  Ethnicity & 3 & 20.00 & 32 & 129.43 & 3.75 & 0.0285 \\ 
  NZDep & 1 & 10.70 & 31 & 118.74 & 6.02 & 0.0239 \\ 
  Age:Ethnicity & 12 & 81.91 & 19 & 36.83 & 3.84 & 0.0045 \\ 
   \hline
\end{tabular}\caption{Significance of different predictor variables for measles risk factors from 2007-2014, estimated using \autoref{eq:reg} and a quasipoisson error structure}
\label{table:anova}
\end{table}
\vspace{5mm} %5mm vertical space

@@

\vspace{5mm} %5mm vertical space
\begin{table}
% latex table generated in R 3.0.2 by xtable 1.7-1 package
% Mon Nov 10 12:38:31 2014
\begin{tabular}{rrrrr}
  \hline
 & Estimate & Std. Error & t value & Pr($>$$|$t$|$) \\ 
  \hline
(Intercept) & -6.4674 & 0.1148 & -56.32 & 0.0000 \\ 
  Age3-5 & -0.9129 & 0.2054 & -4.44 & 0.0003 \\ 
  Age6-17 & -0.7618 & 0.1343 & -5.67 & 0.0000 \\ 
  Age18-24 & -1.5050 & 0.1937 & -7.77 & 0.0000 \\ 
  Age25+ & -2.9507 & 0.1608 & -18.35 & 0.0000 \\ 
  EthnicityAsian & 0.0530 & 0.3250 & 0.16 & 0.8721 \\ 
  EthnicityMaori & 0.2124 & 0.1994 & 1.07 & 0.2999 \\ 
  EthnicityPacific & 1.1603 & 0.2043 & 5.68 & 0.0000 \\ 
  NZDep6-10 & -0.2119 & 0.0855 & -2.48 & 0.0227 \\ 
  Age3-5:EthnicityAsian & -2.0315 & 1.3827 & -1.47 & 0.1581 \\ 
  Age6-17:EthnicityAsian & -1.0074 & 0.4717 & -2.14 & 0.0459 \\ 
  Age18-24:EthnicityAsian & -0.8311 & 0.5941 & -1.40 & 0.1779 \\ 
  Age25+:EthnicityAsian & 0.4211 & 0.4433 & 0.95 & 0.3541 \\ 
  Age3-5:EthnicityMaori & -0.3864 & 0.4096 & -0.94 & 0.3573 \\ 
  Age6-17:EthnicityMaori & -0.0855 & 0.2469 & -0.35 & 0.7328 \\ 
  Age18-24:EthnicityMaori & -0.5828 & 0.4484 & -1.30 & 0.2092 \\ 
  Age25+:EthnicityMaori & -1.0482 & 0.5242 & -2.00 & 0.0600 \\ 
  Age3-5:EthnicityPacific & -2.1316 & 0.8139 & -2.62 & 0.0169 \\ 
  Age6-17:EthnicityPacific & -1.4541 & 0.3347 & -4.35 & 0.0003 \\ 
  Age18-24:EthnicityPacific & -0.9827 & 0.5129 & -1.92 & 0.0705 \\ 
  Age25+:EthnicityPacific & -0.6127 & 0.4367 & -1.40 & 0.1767 \\ 
   \hline
\end{tabular}\caption{Summary of the regression model results for measles risk factors for cases from 2007-2014}
\label{table:regression_riskfactors}
\end{table}
\vspace{5mm} %5mm vertical space

@@

\begin{figure}
\begin{center}
\includegraphics{draftfinalreport-020}
\end{center}
\caption{Age and vaccination status of measles cases, 2007--2014}
\label{fig:ageandvac}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics{draftfinalreport-021}
\end{center}
\caption{Age of vaccination of vaccinated measles cases, 2007--2014}
\label{fig:vaccstat}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics{draftfinalreport-037}
\end{center}
\caption{Measles incidence per million, 2012. Data: WHO (\href{http://www.who.int/research/en/}{www.who.int/research/en/}). Grey indicates not reported.}
\label{fig:incidence12}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics{draftfinalreport-038}
\end{center}
\caption{Measles vaccination cover (\%), 2012. Data: WHO (\href{http://www.who.int/research/en/}{www.who.int/research/en/}). Grey indicates not reported.}
\label{fig:cover12}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics{draftfinalreport-039}
\end{center}
\caption{Non-New Zealander international travel and immigration, 2012 }
\label{fig:immigration12}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics{draftfinalreport-040}
\end{center}
\caption{New Zealander international travel, 2012 }
\label{fig:nztravel12}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics{draftfinalreport-041}
\end{center}
\caption{Total international travel, 2012 }
\label{fig:travel12}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics{draftfinalreport-042}
\end{center}
\caption{Risk map for measles importation, 2012 }
\label{fig:risk12}
\end{figure}

>>>>

\usepackage{Sweave}
\begin{document}
\input{draftfinalreport_v2-concordance}

@@

% \begin{figure}
% \begin{center}
% <<fig=TRUE,echo=FALSE,width = 15,height=12>>=
% par(mfrow=c(1,1))
% par(mar=c(5,6,4,2)+0.1)
% par(cex.axis=2)
% hist(time$AgeInYears,col="grey",xlab="Age in years",main="",breaks=90,include.lowest=TRUE,right=F,ylab="Frequency",cex.lab=2)
% hist(test$AgeInYears,col="black",breaks=90,include.lowest=TRUE,right=F,add=T)
% legend("topright",c("1997-2014","2007-2014"),col=c("grey","black"),pch=15,bty="n",cex=2)
% @
% \end{center}
% \caption{Numbers and age of measles cases in years in New Zealand for two periods, 1997--2014 and 2007--2014}
% \label{fig:ageinyears}
% \end{figure}

@@

% \begin{figure}
% \begin{center}
% <<fig=TRUE,echo=FALSE,width = 15,height=12>>=
% par(mfrow=c(1,1))
% par(mar=c(5,6,4,2)+0.1)
% par(cex.axis=2)
% hist(time$AgeInYears,col="grey",xlab="Age in years",main="",breaks=90,include.lowest=TRUE,right=F,ylab="Frequency",cex.lab=2)
% hist(test$AgeInYears,col="black",breaks=90,include.lowest=TRUE,right=F,add=T)
% legend("topright",c("1997-2014","2007-2014"),col=c("grey","black"),pch=15,bty="n",cex=2)
% @
% \end{center}
% \caption{test}
% %\label{fig:test}
% \end{figure}

% \begin{figure}
% \begin{center}
% <<fig=TRUE,echo=FALSE,width = 15,height=12>>=
% ggplot(tp, aes(NZDep, cases, fill=Age)) + 
%   geom_bar(stat="identity", position="dodge")+
%  # theme(text=element_text(size=45))+
%   ylab("cases")
% @
% \end{center}
% \caption{test}
% %\label{fig:test}
% \end{figure}
% 
% \begin{figure}
% \begin{center}
% <<fig=TRUE,echo=FALSE,width = 15,height=12>>=
% ggplot(tp, aes(NZDep, cases, fill=Ethnicity)) + 
%   geom_bar(stat="identity", position="dodge")+
% #  theme(text=element_text(size=45))+
%   ylab("cases")
% @
% \end{center}
% \caption{test}
% %\label{fig:test}
% \end{figure}
% 
% \begin{figure}
% \begin{center}
% <<fig=TRUE,echo=FALSE,width = 15,height=12>>=
% ggplot(tp, aes(Age, cases, fill=Ethnicity)) + 
%   geom_bar(stat="identity", position="dodge")+
% #  theme(text=element_text(size=45))+
%   ylab("cases")
% @
% \end{center}
% \caption{test}
% %\label{fig:test}
% \end{figure}
% 
% \begin{figure}
% \begin{center}
% <<fig=TRUE,echo=FALSE,width = 15,height=12>>=
% ggplot(tp, aes(NZDep, perCap, fill=Age)) + 
%   geom_bar(stat="identity", position="dodge")+
%  # theme(text=element_text(size=45))+
%   ylab("Per capita per 10000")
% @
% \end{center}
% \caption{test}
% %\label{fig:test}
% \end{figure}
% 
% \begin{figure}
% \begin{center}
% <<fig=TRUE,echo=FALSE,width = 15,height=12>>=
% ggplot(tp, aes(NZDep, perCap, fill=Ethnicity)) + 
%   geom_bar(stat="identity", position="dodge")+
%   #theme(text=element_text(size=45))+
%   ylab("Per capita per 10000")
% @
% \end{center}
% \caption{test}
% %\label{fig:test}
% \end{figure}
% 
% \begin{figure}
% \begin{center}
% <<fig=TRUE,echo=FALSE,width = 15,height=12>>=
% ggplot(tp, aes(Age, perCap, fill=Ethnicity)) + 
%   geom_bar(stat="identity", position="dodge")+
%   #theme(text=element_text(size=45))+
%   ylab("Per capita per 10000")
% @
% \end{center}
% \caption{test}
% %\label{fig:test}
% \end{figure}

% \begin{figure}
% \begin{center}
% <<fig=TRUE,echo=FALSE,width = 15,height=12>>=
% ggplot(tpsub, aes(NZDep, perCap, fill=Age)) + 
%   geom_bar(stat="identity", position="dodge")+
%   #theme(text=element_text(size=45))+
%   ylab("Per capita per 10000")
% @
% \end{center}
% \caption{test}
% %\label{fig:test}
% \end{figure}
% 
% \begin{figure}
% \begin{center}
% <<fig=TRUE,echo=FALSE,width = 15,height=12>>=
% ggplot(tpsub, aes(NZDep, perCap, fill=Ethnicity)) + 
%   geom_bar(stat="identity", position="dodge")+
%   #theme(text=element_text(size=45))+
%   ylab("Per capita per 10000")
% @
% \end{center}
% \caption{test}
% %\label{fig:test}
% \end{figure}
% 
% \begin{figure}
% \begin{center}
% <<fig=TRUE,echo=FALSE,width = 15,height=12>>=
% ggplot(tpsub, aes(Age, perCap, fill=Ethnicity)) + 
%   geom_bar(stat="identity", position="dodge")+
%   #theme(text=element_text(size=45))+
%   ylab("Per capita per 10000")
% @
% \end{center}
% \caption{test}
% %\label{fig:test}
% \end{figure}

% \begin{figure}
% \begin{center}
% <<fig=TRUE,echo=FALSE,width = 15,height=12>>=
% par(cex.axis=2)
% par(mar=c(5,6,4,2)+0.1)
% hist(tpsub$cases,xlab="Number of cases",main='',col='grey',breaks=20,ylab="Number of categories",cex.lab=2)
% @
% \end{center}
% \caption{test}
% %\label{fig:test}
% \end{figure}

% \begin{figure}
% \begin{center}
% <<fig=TRUE,echo=FALSE,width = 15,height=12>>=
% par(mar=c(5,6,4,2)+0.1)
% par(cex.axis=2)
% plot(exp(res),tpsub$cases,xlab="cases",ylab='predictions',main="",pch=16,col="darkgrey",cex.lab=2,cex=2)
% @
% \end{center}
% \caption{test}
% %\label{fig:test}
% \end{figure}

% \begin{figure}
% \begin{center}
% <<fig=TRUE,echo=FALSE,width = 15,height=12>>=
% par(mar=c(5,6,4,2)+0.1)
% par(cex.axis=2)
% #hist(model3$residuals,main="",xlab="residuals",col="grey",cex.lab=2,ylab="")
% hist(model2$residuals,main="",xlab="residuals",col="grey",cex.lab=2,ylab="")
% @
% \end{center}
% \caption{test}
% %\label{fig:test}
% \end{figure}

% \begin{figure}
% \begin{center}
% <<fig=TRUE,echo=FALSE,width = 15,height=12>>=
% par(mar=c(5,6,4,2)+0.1)
% par(cex.axis=2)
% barplot(t(AgeVac),xlab="Age",col=c("darkgrey","red","orange"),main="",ylab="Frequency",cex.lab=2)
% legend("topright",c("Unvaccinated","Dose 1","Dose 2"),fill=c("darkgrey","red","orange"),cex=1.8,bty="n")
% @
% \end{center}
% \caption{test}
% %\label{fig:test}
% \end{figure}
% 
% \begin{figure}
% \begin{center}
% <<fig=TRUE,echo=FALSE,width = 15,height=12>>=
% par(mar=c(5,6,4,2)+0.1)
% par(cex.axis=2)
% hist(vac$Dose1Mths,breaks=100,col=rgb(0,0,1,1/4),xlab="Age in months",main="",cex.lab=2,ylab="Frequency")
% abline(v=12,col="blue")
% hist(vac$Dose2Mths,breaks=50,add=T,col=rgb(1,0,0,1/4))
% abline(v=60,col="red")
% legend("topright",c("Dose 1","Dose 2"),col=c(rgb(0,0,1,1/4),rgb(1,0,0,1/4)),pch=15,bty="n",cex=1.8)
% legend("top",c("12 months","60 months"),col=c("blue","red"),lty=1,bty="n",cex=1.8)
% @
% \end{center}
% \caption{test}
% %\label{fig:test}
% \end{figure}

% \begin{figure}
% \begin{center}
% <<fig=TRUE,echo=FALSE,width = 15,height=12>>=
% par(mar=c(5,6,4,2)+0.1)
% par(cex.axis=1)
% barplot(t(DOBVac),xlab="Age",col=c("darkgrey","red","orange"),main="",ylab="Frequency",cex.lab=1)
% legend("topleft",c("Unvaccinated","Dose 1","Dose 2"),fill=c("darkgrey","red","orange"),cex=1,bty="n")
% @
% \end{center}
% \caption{test}
% %\label{fig:test}
% \end{figure}
% 
% \begin{figure}
% \begin{center}
% <<fig=TRUE,echo=FALSE,width = 15,height=12>>=
% par(mar=c(5,6,4,2)+0.1)
% par(cex.axis=1)
% par(mfrow=c(2,1))
% barplot(DOBVac[,2],col=rgb(0,0,1,1/4),xlab="Date of Birth",main="",cex.lab=1,ylab="Frequency")
% legend("topleft",c("Dose 1"),col=rgb(0,0,1,1/4),pch=15,bty="n",cex=1)
% par(mar=c(5,6,4,2)+0.1)
% par(cex.axis=1)
% barplot(DOBVac[,3],col=rgb(1,0,0,1/4),xlab="Date of Birth",main="",cex.lab=1,ylab="Frequency")
% legend("topleft",c("Dose 2"),col=rgb(1,0,0,1/4),pch=15,bty="n",cex=1)
% @
% \end{center}
% \caption{test}
% %\label{fig:test}
% \end{figure}
% 
% \begin{figure}
% \begin{center}
% <<fig=TRUE,echo=FALSE,width = 15,height=12>>=
% par(mar=c(5,6,4,2)+0.1)
% par(cex.axis=1.5)
% par(mfrow=c(1,1))
% barplot(DOBVac[,1],col="grey",xlab="Date of Birth",main="",cex.lab=1.5,ylab="Frequency")
% legend("topleft",c("Unvaccinated"),col="grey",pch=15,bty="n",cex=1.5)
% @
% \end{center}
% \caption{test}
% %\label{fig:test}
% \end{figure}

% \begin{figure}
% \begin{center}
% <<fig=TRUE,echo=FALSE,width = 15,height=12>>=
% par(cex.axis=2)
% par(mar=c(5,6,4,2)+0.1)
% plot(pop,xlab="Age",ylab="Population",cex.lab=2)
% points(naive,pch=16)
% legend("topright",c("Population","Naive"),pch=c(1,16),bty="n",cex=1.8)
% @
% \end{center}
% \caption{test}
% %\label{fig:test}
% \end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics{draftfinalreport_v2-019}
\end{center}
\caption{Per capita rates of measles infections for specific age categories (0--2, 3--5, 6--17, 18--24, and 24+ years) and New Zealand deprivation indices (NZDep, 1--5 and 6--10) for 2007--2014, broken down by ethnicity (\autoref{table:percap} for details)}
\label{fig:percap}
\end{figure}

\begin{table}[hbtp]
\footnotesize
\caption{Numbers of measles cases (Cases), population sizes (Ppulation) and per capita rates per 10,000 (Per capita) of measles in specific age (Age), ethnicity (Ethnicity) and socio-economic deprivation (NZDep) categories from 2007-2014}
%latex.default(PerCap, file = "", table.env = FALSE, rowname = NULL)%
\begin{tabular}{lllrrr}
\hline\hline
\multicolumn{1}{c}{NZDep}&\multicolumn{1}{c}{Age}&\multicolumn{1}{c}{Ethnicity}&\multicolumn{1}{c}{Population}&\multicolumn{1}{c}{Cases 1}&\multicolumn{1}{c}{Per capita}\tabularnewline
\hline
1-3&0-1&Asian&$  2269$&$  6$&$26.4434$\tabularnewline
4-7&0-1&Asian&$  3748$&$ 10$&$26.6809$\tabularnewline
8-10&0-1&Asian&$  2583$&$  3$&$11.6144$\tabularnewline
1-3&2-4&Asian&$  3403$&$  1$&$ 2.9386$\tabularnewline
4-7&2-4&Asian&$  5623$&$  0$&$ 0.0000$\tabularnewline
8-10&2-4&Asian&$  3874$&$  0$&$ 0.0000$\tabularnewline
1-3&5-17&Asian&$ 20625$&$  6$&$ 2.9091$\tabularnewline
4-7&5-17&Asian&$ 29721$&$  8$&$ 2.6917$\tabularnewline
8-10&5-17&Asian&$ 16777$&$  2$&$ 1.1921$\tabularnewline
1-3&18-24&Asian&$ 12057$&$  2$&$ 1.6588$\tabularnewline
4-7&18-24&Asian&$ 23904$&$  3$&$ 1.2550$\tabularnewline
8-10&18-24&Asian&$ 21063$&$  3$&$ 1.4243$\tabularnewline
1-3&25+&Asian&$ 54258$&$  4$&$ 0.7372$\tabularnewline
4-7&25+&Asian&$ 86055$&$ 11$&$ 1.2783$\tabularnewline
8-10&25+&Asian&$ 54759$&$  8$&$ 1.4609$\tabularnewline
1-3&0-1&European&$ 23961$&$ 40$&$16.6938$\tabularnewline
4-7&0-1&European&$ 28051$&$ 58$&$20.6766$\tabularnewline
8-10&0-1&European&$ 16866$&$ 24$&$14.2298$\tabularnewline
1-3&2-4&European&$ 35942$&$ 37$&$10.2944$\tabularnewline
4-7&2-4&European&$ 42076$&$ 22$&$ 5.2286$\tabularnewline
8-10&2-4&European&$ 25299$&$  6$&$ 2.3716$\tabularnewline
1-3&5-17&European&$180875$&$160$&$ 8.8459$\tabularnewline
4-7&5-17&European&$194100$&$118$&$ 6.0793$\tabularnewline
8-10&5-17&European&$106731$&$ 40$&$ 3.7477$\tabularnewline
1-3&18-24&European&$ 63051$&$ 24$&$ 3.8064$\tabularnewline
4-7&18-24&European&$ 94422$&$ 26$&$ 2.7536$\tabularnewline
8-10&18-24&European&$ 68016$&$ 20$&$ 2.9405$\tabularnewline
1-3&25+&European&$619698$&$ 54$&$ 0.8714$\tabularnewline
4-7&25+&European&$734550$&$ 46$&$ 0.6262$\tabularnewline
8-10&25+&European&$371985$&$ 29$&$ 0.7796$\tabularnewline
1-3&0-1&Maori&$  3265$&$  9$&$27.5651$\tabularnewline
4-7&0-1&Maori&$  8378$&$ 13$&$15.5168$\tabularnewline
8-10&0-1&Maori&$ 15094$&$ 32$&$21.2005$\tabularnewline
1-3&2-4&Maori&$  4897$&$  4$&$ 8.1683$\tabularnewline
4-7&2-4&Maori&$ 12568$&$ 12$&$ 9.5481$\tabularnewline
8-10&2-4&Maori&$ 22642$&$ 10$&$ 4.4166$\tabularnewline
1-3&5-17&Maori&$ 21750$&$  8$&$ 3.6782$\tabularnewline
4-7&5-17&Maori&$ 53963$&$ 33$&$ 6.1153$\tabularnewline
8-10&5-17&Maori&$ 94758$&$ 74$&$ 7.8094$\tabularnewline
1-3&18-24&Maori&$  7329$&$  3$&$ 4.0933$\tabularnewline
4-7&18-24&Maori&$ 20862$&$  2$&$ 0.9587$\tabularnewline
8-10&18-24&Maori&$ 35664$&$  8$&$ 2.2432$\tabularnewline
1-3&25+&Maori&$ 35934$&$  1$&$ 0.2783$\tabularnewline
4-7&25+&Maori&$ 87192$&$  3$&$ 0.3441$\tabularnewline
8-10&25+&Maori&$140820$&$  4$&$ 0.2841$\tabularnewline
1-3&0-1&MLA&$   273$&$  0$&$ 0.0000$\tabularnewline
4-7&0-1&MLA&$   519$&$  2$&$38.5356$\tabularnewline
8-10&0-1&MLA&$   553$&$  1$&$18.0832$\tabularnewline
1-3&2-4&MLA&$   410$&$  0$&$ 0.0000$\tabularnewline
4-7&2-4&MLA&$   778$&$  0$&$ 0.0000$\tabularnewline
8-10&2-4&MLA&$   830$&$  1$&$12.0482$\tabularnewline
1-3&5-17&MLA&$  1832$&$  0$&$ 0.0000$\tabularnewline
4-7&5-17&MLA&$  3121$&$  0$&$ 0.0000$\tabularnewline
8-10&5-17&MLA&$  3250$&$  1$&$ 3.0769$\tabularnewline
1-3&18-24&MLA&$   906$&$  0$&$ 0.0000$\tabularnewline
4-7&18-24&MLA&$  1806$&$  0$&$ 0.0000$\tabularnewline
8-10&18-24&MLA&$  2076$&$  2$&$ 9.6339$\tabularnewline
1-3&25+&MLA&$  4569$&$  0$&$ 0.0000$\tabularnewline
4-7&25+&MLA&$  7452$&$  5$&$ 6.7096$\tabularnewline
8-10&25+&MLA&$  6342$&$  1$&$ 1.5768$\tabularnewline
1-3&0-1&Pacific&$   643$&$  1$&$15.5521$\tabularnewline
4-7&0-1&Pacific&$  2113$&$  6$&$28.3956$\tabularnewline
8-10&0-1&Pacific&$  7389$&$ 48$&$64.9614$\tabularnewline
1-3&2-4&Pacific&$   964$&$  0$&$ 0.0000$\tabularnewline
4-7&2-4&Pacific&$  3169$&$  1$&$ 3.1556$\tabularnewline
8-10&2-4&Pacific&$ 11084$&$ 10$&$ 9.0220$\tabularnewline
1-3&5-17&Pacific&$  4212$&$  2$&$ 4.7483$\tabularnewline
4-7&5-17&Pacific&$ 13419$&$  4$&$ 2.9808$\tabularnewline
8-10&5-17&Pacific&$ 47165$&$ 21$&$ 4.4525$\tabularnewline
1-3&18-24&Pacific&$  1707$&$  0$&$ 0.0000$\tabularnewline
4-7&18-24&Pacific&$  6174$&$  4$&$ 6.4788$\tabularnewline
8-10&18-24&Pacific&$ 18189$&$  5$&$ 2.7489$\tabularnewline
1-3&25+&Pacific&$  8580$&$  1$&$ 1.1655$\tabularnewline
4-7&25+&Pacific&$ 26688$&$  3$&$ 1.1241$\tabularnewline
8-10&25+&Pacific&$ 74757$&$  9$&$ 1.2039$\tabularnewline
\hline
\end{tabular}\end{center}\label{table:percap}
\end{table}

@@

The distribution of the meases cases per category used in the regression analyses are in \autoref{fig:histcasecat}.
\begin{figure}
\begin{center}
\includegraphics{draftfinalreport_v2-023}
\end{center}
\caption{Distribution of measles cases per category (\autoref{table:percap}) used in the final regression model (\autoref{eq:reg})}
\label{fig:histcasecat}
\end{figure}

The predicted values from the regression model plotted against the reported cases are shown in \autoref{fig:predict}, and the residuals are shown in \autoref{fig:resid}.
\begin{figure}
\begin{center}
\includegraphics{draftfinalreport_v2-024}
\end{center}
\caption{Regression model (\autoref{eq:reg}) predictions plotted against the case data (\autoref{table:percap})}
\label{fig:predict}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics{draftfinalreport_v2-026}
\end{center}
\caption{Histogram of residuals from the regression model (\autoref{eq:reg})}
\label{fig:resid}
\end{figure}

The significance of the different predictor variables can be seen in the ANOVA results (\autoref{table:anova}).
\par
\vspace{5mm} %5mm vertical space
\begin{table}
% latex table generated in R 3.0.2 by xtable 1.7-3 package
% Wed Mar 18 16:47:24 2015
\begin{tabular}{lrrrrrr}
  \hline
 & Df & Deviance & Resid. Df & Resid. Dev & F & Pr($>$F) \\ 
  \hline
NULL &  &  & 59 & 1532.80 &  &  \\ 
  Age & 4 & 1345.17 & 55 & 187.63 & 204.01 & 0.0000 \\ 
  Ethnicity & 3 & 19.88 & 52 & 167.75 & 4.02 & 0.0141 \\ 
  NZDep & 2 & 17.10 & 50 & 150.65 & 5.19 & 0.0102 \\ 
  Age:Ethnicity & 12 & 80.80 & 38 & 69.85 & 4.09 & 0.0004 \\ 
   \hline
\end{tabular}\caption{Significance of different predictor variables for measles risk factors from 2007-2014, estimated using \autoref{eq:reg} and a quasipoisson error structure}
\label{table:anova}
\end{table}
\vspace{5mm} %5mm vertical space

@@

% \vspace{5mm} %5mm vertical space
% \begin{table}
% % <<label=regmodel,include=FALSE,results=tex,echo=FALSE>>=
% % library(xtable)
% % xtb<-xtable(summary(model3))
% % print(xtb,floating = FALSE)
% % @
% \caption{Summary of the regression model results for measles risk factors for cases from 2007-2014}
% \label{table:regression_riskfactors}
% \end{table}
% \vspace{5mm} %5mm vertical space

@@

\begin{figure}
\begin{center}
\includegraphics{draftfinalreport_v2-028}
\end{center}
\caption{Age and vaccination status of measles cases, 2007--2014}
\label{fig:ageandvac}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics{draftfinalreport_v2-029}
\end{center}
\caption{Age of vaccination of vaccinated measles cases, 2007--2014}
\label{fig:vaccstat}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics{draftfinalreport_v2-047}
\end{center}
\caption{Measles incidence per million, 2012. Data: WHO (\href{http://www.who.int/research/en/}{www.who.int/research/en/}). Grey indicates not reported.}
\label{fig:incidence12}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics{draftfinalreport_v2-048}
\end{center}
\caption{Measles vaccination cover (\%), 2012. Data: WHO (\href{http://www.who.int/research/en/}{www.who.int/research/en/}). Grey indicates not reported.}
\label{fig:cover12}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics{draftfinalreport_v2-049}
\end{center}
\caption{Non-New Zealander international travel and immigration, 2012 }
\label{fig:immigration12}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics{draftfinalreport_v2-050}
\end{center}
\caption{New Zealander international travel, 2012 }
\label{fig:nztravel12}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics{draftfinalreport_v2-051}
\end{center}
\caption{Total international travel, 2012 }
\label{fig:travel12}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics{draftfinalreport_v2-052}
\end{center}
\caption{Risk map for measles importation, 2012 }
\label{fig:risk12}
\end{figure}
